\documentclass{article}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lipsum}

\begin{document}

\section{Questions}

\begin{itemize}
  \item Should it output a list or a phrase?
  \item Only ask actionExists questions if object or verb is in video?
  \item Should we output indirect references? 
  \begin{itemize}
      \item Ex: "Which did they start first, the action they did the longest or smiling?" 
      \item Current: holding a blanket
      \item Option:  the action they did the longest
      \item It's a non-trivial fix, and expands our answer space a lot 
  \end{itemize}
\end{itemize}


\section{What's left with templates}
\begin{itemize}
    \item Combining  verbs like “putting something on a table” and “putting a cup somewhere” so not separate if referring to same action
    \item fix grammar and add more grammar capabilities
    \item add more natural language examples for each question
    \item add more indirect references
    \item add more templates (choose/verify, and, xor, or, etc)
    \item balancing for all variables (and test balancing values)
    \item add in code necessary for dividing test set into different groups
    \item better explanations (and subprocesses like "I want to know about x")?
    \item be able to make all of the videos
\end{itemize}

\section{Metrics}
\setlength\LTleft{-1in}
\setlength\LTright{-1in}

\begin{longtable}[]{|p{2cm}|p{4cm}|p{10cm}|}
    %\begin{center}
    \caption{Suite of Metrics}
    \label{tab:table1}
    %\noindent\makebox[\textwidth]{
    %\begin{tabular}{|p{3cm}|p{4cm}|p{10cm}|}
        \hline
        \textbf{Title} & \textbf{Formalized} & \textbf{Description}\\
        \hline
        \multicolumn{3}{|c|}{\textbf{Video Length}}\\
        \hline
        Video Length & Accuracy of $\hat{A}$ on videos of length $>$ X seconds & Trains on short videos and judges on long videos \textbf{Also train on videos with small number of actions and test on a larger number of actions? } \\
        \hline
        \multicolumn{3}{|c|}{\textbf{Content Type}}\\
        \hline
        Global Variables & Accuracy for each global category & Split into larger categories (count, length, sequence, first etc)\\
        \hline
        \multicolumn{3}{|c|}{\textbf{Answer Type}}\\
        \hline
        Chance Accuracy & Accuracy of binary questions and Accuracy of open questions & Split into binary and open questions\\
        \hline
        Question Type & Accuracy for each question structure  & Choose, verify, logical, open, etc\\
        \hline
        \multicolumn{3}{|c|}{\textbf{Lists}}\\
        \hline
        Length & Percent $\hat{a} \in \hat{A}$ where $|\hat{a}| = |a|$ \textbf{Unless should be by how far off it is?} & Check correct length\\
        \hline 
        Similarity & \textbf{How to measure? Levenshtein distance?} & Is the list missing information, containing extra information, and/or containing incorrect information? \\
        \hline
        Ordering & \textbf{(Same question as above)} & For ordered lists, are they just out of order? If only looked at without ordering would the accuracy increase? \\
        \hline
        \multicolumn{3}{|c|}{\textbf{Superlatives}}\\
        \hline
        Superlative Closeness & For all $q$ in first/last category, percent in which $\hat{a} = a$ or $\hat{a}$ is within relevant frames but is not first/last & item given as "first" or "last" still occurred, just wasn't first or last \\
        \hline
        \multicolumn{3}{|c|}{\textbf{Compositionality}}\\
        \hline
        \% Training Data & The accuracy of $\hat{A}$ when trained on X\% of data &
        \% of distinct examples (the total num is constant)\\
        && \textbf{So: I think this is by the number of templates? It's worth testing, but im concerned will be a lot harder than Lake's}  \\
        \hline
        Number Compositional Steps & Accuracy on questions with $\geq$ X steps & Train on $<$ X steps, Test on $\geq$ X step. \textbf{Should be high enough to include all templates?}\\
        \hline
        Novel Compositions & Accuracy on $Q$ where $\forall q \in Q, q$ has an unseen composition& Leave out certain compositions of the below with obj/rel/action and then test\\
        && First and Last\\
        && xor/and and other logical operations \\
        && question structures (choose, verify)\\
        && multi-level indirect (train on "action they did the longest" and "before running". Test on "before the action they did the longest")\\
        && before and after \\
        && more and fewer \\
        && longer and shorter
        &&\\
        && \textbf{Note: Lake et al only did 2, because the others were distributionally identical.}\\
        && \textbf{They only saw a basic action (JUMP)}\\
        \hline
        Indirect Refs & For all questions i with only direct references, $I_i$ is the same question with all indirect tag combinations. Of $(q, a) \in I_i$, measure the percent of $\hat{a} = a$ & Start with all direct refs, and see if it gets it wrong by replacing with any. \textbf{What would the final number be? Should it be by number of indirect refs, or type?}\\
        \hline
        Time Localization & Accuracy on $\hat{a}$ for all $q \in T_i$ where $i \in \{0, 1, 2\}$ and $T_i$ has $i$ temporal localization steps & No localization, One step (before, after, while), Two steps localization (between)\\
        \hline
        \multicolumn{3}{|c|}{\textbf{Answer Legitimacy}}\\
        \hline
        \multirow{1}{*}{Consistent} & $\forall(q, a)$, $E_q = (q_1, a_1),$ $(q_2, a_2), \dots, (q_n, a_n)$ & Answers that are necessarily entailed are correct   \\
        &&\\
        & Score is the Accuracy of $E_q$ for every $(q, a) \in Q$ ($Q$ = questions answered correctly) averaged across $|Q|$& \\
        &&\\
        &\textbf{Would it be helpful to do for incorrect answers too to see where just misidentifying?}& \\
        && x before y $\rightarrow$ y after x \\
        && x longer than y $\rightarrow$ y shorter than x\\
        && x more times than y $\rightarrow$ y fewer times than x\\
        && "No" $\rightarrow$ All AND questions "No"\\
        && x AND y = "Yes" $\rightarrow$ x = "Yes", y = "Yes"\\
        && first is x = "Yes" $\rightarrow$ first is y = "No", and first is x for any temporal localization "before"\\
        && last is x = "Yes" $\rightarrow$ last is y = "No", and last is x for any temporal localization "after"\\
        && \textbf{TODO: entailments with sequences and lists?}\\
        \hline
        Validity & For $a \in \{$given answers$\}$, $a \in V_q$ where $ V_q = $ set of all possible answers in correct genre & Answer type is of correct genre\\
        && Yes/No \\
        && Number \\
        && Before/after \\
        && Object \\
        && Relationship \\
        && Action \\
        && List\\
        \hline
        Plausibility & For $a \in \{$given answers$\}$, $a \in P_q$ where $ P_q = $ set of all answers in answer distribution & Answer within distribution of possible answers\\
        \hline
        Predicted vs Actual Dist &  $\chi^2$ difference between $\hat{A_i}$ and $A_i$ where $A_i$ is the answer distribution for question type $i$. & How close tested answer distribution is from true answer distribution (\textbf{per general type or per exact template?)}\\
        \hline
        Attention Grounding & & Model paying attention to right set of frames \textbf{and right spatial location?} \\
        \hline
        
    %\end{tabular}
    %}
    %\end{center}
\end{longtable}


\end{document}

